---
title: "WSW"
author: "Marco Biella"
date: "2022-11-24"
output:
  pdf_document: default
header-includes:  
- \usepackage{lscape}  
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, comment = "", warning = FALSE, message = FALSE)
```

```{r}
rm(list = ls())

library(tidyverse)
library(ggradar)
library(ggpubr)
library(ggplot2)
library(ggmosaic)
library(patchwork)
library(ggrepel)
library(usedist)
library(bayestestR)
library(bayesplot)
library(brms)
library(qgraph)
library(bootnet)
library(NetworkComparisonTest)
library(gt)
library(IsingFit)

recode_01 <- function(vct, yes = 1, no = 2, offset = -1){
  vct <- -(vct - (yes + no))
  if(!is.null(offset)){
    vct <- vct + offset
    }
  return(vct)
}

apa <- function(x, title = " ") {
  gt(x) %>%
  tab_options(
    table.border.top.color = "white",
    heading.title.font.size = px(16),
    column_labels.border.top.width = 3,
    column_labels.border.top.color = "black",
    column_labels.border.bottom.width = 3,
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table.border.bottom.color = "white",
    table.width = pct(100),
    table.background.color = "white"
  ) %>%
  cols_align(align="center") %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      cell_text(
        align="center"
      ),
      cell_fill(color = "white", alpha = NULL)
      ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
    #title setup
    tab_header(
    title = html("<i>", title, "</i>")
  ) %>%
  opt_align_table_header(align = "left")
}
```

```{r}
dat <- read_csv2(file = "wswSexualPractices.csv",
               ) %>%
  #filter valid and consent
  dplyr::filter(consent == 1) %>%
  #trim variables
  mutate(id = 1:n()) %>%
  dplyr::select(
    id,
    age, relation, edu, 
    WSW, sex_attr, rom_attr, self_def, 
    LIHS_1, LIHS_2, LIHS_3, LIHS_4, LIHS_5, LIHS_6, LIHS_7, LIHS_8, 
    LIHS_9, LIHS_10, LIHS_11, LIHS_12, 
    SQoL_1, SQoL_2, SQoL_3, SQoL_4, SQoL_5, SQoL_6, SQoL_7, SQoL_8, 
    SQoL_9, SQoL_10, SQoL_11, SQoL_12, SQoL_13, SQoL_14, SQoL_15, 
    SQoL_16, SQoL_17, SQoL_18, 
    insertive, insertive_no, insertive_yes_1_1, insertive_yes_1_2,
    insertive_yes_1_3, insertive_yes_1_4, insertive_yes_1_5, insertive_yes_1_6, 
    oral, oral_no, oral_yes_1_1, oral_yes_1_2, oral_yes_1_3, oral_yes_1_4, 
    oral_yes_1_5, oral_yes_1_6, 
    masturbation, masturbation_no, masturbation_yes_1_1, masturbation_yes_1_2, 
    masturbation_yes_1_3, masturbation_yes_1_4, masturbation_yes_1_5, 
    masturbation_yes_1_6, 
    finger, finger_no, finger_yes_1_1, finger_yes_1_2, finger_yes_1_3, 
    finger_yes_1_4, finger_yes_1_5, finger_yes_1_6, 
    anal, anal_no, anal_yes_1_1, anal_yes_1_2, anal_yes_1_3, anal_yes_1_4, 
    anal_yes_1_5, anal_yes_1_6, 
    petting_no, petting_1, petting_2, petting_3,
    petting_yes_1_1, petting_yes_1_2, petting_yes_1_3, petting_yes_1_4, petting_yes_1_5, 
    intercrural, intercrural_no, intercrural_yes_1_1, intercrural_yes_1_2, 
    intercrural_yes_1_3, intercrural_yes_1_4, intercrural_yes_1_5, 
    kink, kink_no, kink_yes_1_1, kink_yes_1_2, kink_yes_1_3, kink_yes_1_4,
    kink_yes_1_5, kink_yes_1_6, 
    kink_practices_1, kink_practices_2, kink_practices_3, kink_practices_4, 
    kink_practices_5, kink_practices_6, kink_practices_7, kink_practices_8, 
    kink_practices_9, kink_practices_10, kink_practices_11, kink_practices_12, 
    kink_practices_13, kink_practices_14, kink_practices_15, kink_practices_16, 
    kink_practices_17, kink_practices_18, kink_practices_19, kink_practices_20, 
    kink_practices_21, kink_practices_22, kink_practices_23, kink_practices_24, 
    kink_practices_25, kink_practices_26, kink_practices_27, kink_practices_28, 
    kink_practices_29, 
    chemsex, chemsex_no, chemsex_yes_1_1, chemsex_yes_1_2, chemsex_yes_1_3, 
    chemsex_yes_1_4, chemsex_yes_1_5, chemsex_yes_1_6,
    chemsex_sub1_1, chemsex_sub1_2, chemsex_sub1_3, chemsex_sub2_1, chemsex_sub2_2, 
    chemsex_sub2_3, chemsex_sub2_4, chemsex_sub2_5, chemsex_sub2_6, chemsex_sub2_7, 
    chemsex_sub2_8, chemsex_sub2_9, chemsex_sub2_10, chemsex_sub2_11, chemsex_sub2_12, 
    sub_nosex, sub_type_2, sub_type_3, sub_type_4, sub_type_5, sub_type_6, 
    sub_type_7, sub_type_8, sub_type_9, sub_type_10, sub_type_11, 
    Q45_1, Q45_2, Q45_3, Q45_4, Q45_5, 
    other,
    insertive_new, oral_new, masturbation_new, finger_new, anal_new, 
    intercrural_new, kink_new, insertive_toy, oral_toy, masturbation_toy, 
    finger_toy, petting_toy, anal_toy, intercrural_toy, kink_toy, insertive_lube, 
    oral_lube, masturbation_lube, finger_lube, anal_lube, petting_lube, 
    intercrural_lube, kink_lube, insertive_prot, oral_prot, masturbation_prot, 
    finger_prot, anal_prot, kink_prot, insertive_partner, oral_partner, 
    masturbation_partner, finger_partner, anal_partner, petting_partner, 
    intercrural_partner, kink_partner, insertive_occasional, oral_occasional, 
    masturbation_occasional, finger_occasional, anal_occasional, petting_occasional, 
    intercrural_occasional, kink_occasional,
    insertive_wsw, oral_wsw, masturbation_wsw, finger_wsw, anal_wsw, 
    petting_wsw, intercrural_wsw, kink_wsw, 
    Exp_Index, toy_index, lube_index, prot_index, partner_index, 
    occasion_index, wsw_index
    ) %>%
  #compute petting (multiple choice)
  rename(
    petting_noinsertive = petting_1,
    petting_foreplay = petting_2) %>%
  #rename variables
  rename(
    substances_1 = Q45_1,
    substances_2 = Q45_2,
    substances_3 = Q45_3,
    substances_4 = Q45_4,
    substances_5 = Q45_5,
    ) %>%
  #recode values
  mutate(
    age = as.numeric(age) + 16,
    self_def = case_when(
      self_def == 1 ~ "lesbian",
      self_def == 2 ~ "bisexual",
      self_def == 3 ~ "etero",
    )
  ) %>%
  #recode yes and no
  mutate(
    insertive = recode_01(vct = insertive),
    oral = recode_01(vct = oral),
    masturbation = recode_01(vct = masturbation),
    finger = recode_01(vct = finger),
    anal = recode_01(vct = anal),
    intercrural = recode_01(vct = intercrural),
  ) %>%
  #replace missings as "no"
  replace_na(list(petting_noinsertive = 0, petting_foreplay = 0, finger = 0))
```

## Sociodemographics  

```{r}
#tidying for sociodemo
dat <- dat %>%
  mutate(
    edu = case_when(
      edu == 1 ~ "1_elementary school",
      edu == 2 ~ "2_middle school",
      edu == 3 ~ "3_professional certificate",
      edu == 4 ~ "4_high school",
      edu == 5 ~ "5_degree",
      edu == 6 ~ "6_other",
      edu == 7 ~ "7_don't want to answer",),
    relation = case_when(
      relation == 1 ~ "1_monogamy",
      relation == 2 ~ "2_enm",
      relation == 3 ~ "3_enm_nonconsensual",
      relation == 4 ~ "4_single",
      relation == 5 ~ "5_single_enm",
      relation == 6 ~ "6_none",
      relation == 7 ~ "7_other",),
    sex_attr = case_when(
      sex_attr == 1 ~ "1_exclusively women",
      sex_attr == 2 ~ "2_mostly women, occasionally men",
      sex_attr == 3 ~ "3_mostly women, substantially men",
      sex_attr == 4 ~ "4_equally",
      sex_attr == 5 ~ "5_mostly men, substantially women",
      sex_attr == 6 ~ "6_mostly men, occasionally women",
      sex_attr == 7 ~ "7_exclusively men",
      sex_attr == 8 ~ "8_neither",
      sex_attr == 9 ~ "9_gender is irrelevant",
      sex_attr == 10 ~ "10_other",
      sex_attr == 11 ~ "11_don't want to answer",),
    rom_attr = case_when(
      rom_attr == 1 ~ "1_exclusively women",
      rom_attr == 2 ~ "2_mostly women, occasionally men",
      rom_attr == 3 ~ "3_mostly women, substantially men",
      rom_attr == 4 ~ "4_equally",
      rom_attr == 5 ~ "5_mostly men, substantially women",
      rom_attr == 6 ~ "6_mostly men, occasionally women",
      rom_attr == 7 ~ "7_exclusively men",
      rom_attr == 8 ~ "8_neither",
      rom_attr == 9 ~ "9_gender is irrelevant",
      rom_attr == 10 ~ "10_other",
      rom_attr == 11 ~ "11_don't want to answer",),
    )
```

Age  

```{r}
c(summary(dat$age)[c("Min.", "Max.", "Mean")], "Sd" = sd(dat$age)) %>%
  round(digits = 2)
```

Education  

```{r}
eduDesc <- rbind(table(dat$edu),
      round((table(dat$edu) / nrow(dat)) * 100, digits = 2)) %>%
  t()
colnames(eduDesc) <- c("absolute frequency", "relative frequency")
eduDesc
```

Relationship  

```{r}
relDesc <- rbind(table(dat$relation),
                 round((table(dat$relation) / nrow(dat)) * 100, digits = 2)) %>%
  t()
colnames(relDesc) <- c("absolute frequency", "relative frequency")
relDesc
```

Sexual attraction  

```{r}
attrDesc <- rbind(table(dat$sex_attr), 
                  round((table(dat$sex_attr) / nrow(dat)) * 100, digits = 2)) %>% 
  t()
colnames(attrDesc) <- c("absolute frequency", "relative frequency")
attrDesc
```

Ad-hoc: Sexual attraction

```{r}
attrDesc_adhoc <- dat %>%
  mutate(
    sex_attr = case_when(
      sex_attr == "1_exclusively women" ~ "1_leaning toward women",
      sex_attr == "2_mostly women, occasionally men" ~ "1_leaning toward women",
      sex_attr == "3_mostly women, substantially men" ~ "1_leaning toward women",
      sex_attr == "4_equally" ~ "4_equally",
      sex_attr == "5_mostly men, substantially women" ~ "5_leaning toward men",
      sex_attr == "6_mostly men, occasionally women" ~ "5_leaning toward men",
      sex_attr == "7_exclusively men" ~ "5_leaning toward men",
      sex_attr == "8_neither" ~ "8_neither",
      sex_attr == "9_gender is irrelevant" ~ "9_gender is irrelevant",
      sex_attr == "10_other" ~ "10_other",
      sex_attr == "11_don't want to answer" ~ "11_don't want to answer")) %>%
  dplyr::select(sex_attr)
attrDesc_adhoc <- rbind(table(attrDesc_adhoc$sex_attr), 
                  round((table(attrDesc_adhoc$sex_attr) / nrow(attrDesc_adhoc)) * 100, digits = 2)) %>% 
  t()
colnames(attrDesc_adhoc) <- c("absolute frequency", "relative frequency")
attrDesc_adhoc
```

Romantic attraction  

```{r}
romDesc <- rbind(table(dat$rom_attr), 
                  round((table(dat$rom_attr) / nrow(dat)) * 100, digits = 2)) %>% 
  t()
colnames(romDesc) <- c("absolute frequency", "relative frequency")
romDesc
```

Ad-hoc: Romantic attraction

```{r}
romDesc_adhoc <- dat %>%
  mutate(
    rom_attr = case_when(
      rom_attr == "1_exclusively women" ~ "1_exclusively women",
      rom_attr == "2_mostly women, occasionally men" ~ "2_mostly women",
      rom_attr == "3_mostly women, substantially men" ~ "2_mostly women",
      rom_attr == "4_equally" ~ "4_equally",
      rom_attr == "5_mostly men, substantially women" ~ "5_leaning toward men",
      rom_attr == "6_mostly men, occasionally women" ~ "5_leaning toward men",
      rom_attr == "7_exclusively men" ~ "5_leaning toward men",
      rom_attr == "8_neither" ~ "8_neither",
      rom_attr == "9_gender is irrelevant" ~ "9_gender is irrelevant",
      rom_attr == "10_other" ~ "10_other",
      rom_attr == "11_don't want to answer" ~ "11_don't want to answer")) %>%
  dplyr::select(rom_attr)
romDesc_adhoc <- rbind(table(romDesc_adhoc$rom_attr), 
                  round((table(romDesc_adhoc$rom_attr) / nrow(romDesc_adhoc)) * 100, digits = 2)) %>% 
  t()
colnames(romDesc_adhoc) <- c("absolute frequency", "relative frequency")
romDesc_adhoc
```

Sexual orientation  

```{r}
sexDesc <- rbind(table(dat$self_def),
                 round((table(dat$self_def) / nrow(dat)) * 100, digits = 2)) %>%
  t()
colnames(sexDesc) <- c("absolute frequency", "relative frequency")
sexDesc
```


## Inference on frequency in the population  

Descriptive disaggregated  

```{r}
popul_pract_global <- dat %>%
  dplyr::select(insertive, oral, masturbation, finger, anal,
                intercrural, kink, petting_noinsertive, petting_foreplay) %>%
  gather(key = "practice", value = "response") %>%
  dplyr::filter(complete.cases(.)) %>%
  group_by(practice, response) %>%
  summarise(respCount = n()) %>%
  ungroup() %>% 
  mutate(
    response = ifelse(response == 1, no = "no", yes = "yes")) %>%
  spread(key = "response", value = "respCount", fill = 0) %>%
  mutate(relative_incidence = ((yes / (yes + no)) * 100))
popul_pract_global %>%
  as.data.frame() %>%
  mutate(relative_incidence = round(relative_incidence, digits = 2)) %>%
  arrange(desc(relative_incidence))
```

Inference aggregated  

```{r}
#compute and store practice incidence
popul_pract <- dat %>%
  dplyr::select(self_def,
                insertive, oral, masturbation, finger, anal,
                intercrural, kink, petting_noinsertive, petting_foreplay) %>%
  gather(key = "practice", value = "response", -self_def) %>%
  dplyr::filter(complete.cases(.)) %>%
  group_by(self_def, practice, response) %>%
  summarise(respCount = n()) %>%
  ungroup() %>% 
  mutate(
    response = ifelse(response == 1, no = "no", yes = "yes")) %>%
  spread(key = "response", value = "respCount", fill = 0)
popul_pract$populProp = popul_pract$yes / (popul_pract$yes + popul_pract$no)
popul_pract$confInt_low <- NA
popul_pract$confInt_up <- NA
posteriorSamples <- list()
set.seed(20230127)
for(i in 1:nrow(popul_pract)){
  #extract beta parameters
  a = popul_pract[i, "yes"] %>% unlist() %>% unname()
  b = popul_pract[i, "no"] %>% unlist() %>% unname()
  #extract population features
  grp = popul_pract[i, "self_def"] %>% unlist() %>% unname()
  prtc = popul_pract[i, "practice"] %>% unlist() %>% unname()
  #introduce .1 instead of 0
  if(a == 0){a = .1}
  if(b == 0){b = .1}
  #simulated posterior
  # generate a beta distribution
  posterior_sim <- distribution_beta(n = 100000, shape1 = a, shape2 = b)
  posterior_sim <- sample(x = posterior_sim,
                          size = length(posterior_sim),
                          replace = TRUE) #shuffle
  # compute HDI
  ci_hdi <- ci(x = posterior_sim, method = "HDI")
  #store
  popul_pract[i, "confInt_low"] = ci_hdi$CI_low
  popul_pract[i, "confInt_up"] = ci_hdi$CI_high
  posteriorSamples[[grp]][[prtc]] = posterior_sim
  #clean
  rm(a, b, grp, prtc, posterior_sim, ci_hdi)
};rm(i)
#visual
ggplot(data = popul_pract,
       aes(x = self_def, y = populProp,
           ymax = confInt_up, ymin = confInt_low,
           color = self_def)) +
  geom_hline(yintercept = 1) +
  facet_wrap(practice ~ .) +
  geom_point() +
  geom_errorbar(width = .25) +
  scale_color_discrete(type = c("#eb9b34", "dark green", "#2828ed")) +
  coord_cartesian(ylim = c(.04, .96)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = .1)) +
  labs(y = "proportion", x = "self identification") +
  theme_pubclean() +
  theme(panel.border = element_rect(color = "black", fill = NA),
        legend.position = "none")
incidencePlot <- ggplot(data = popul_pract %>%
                          dplyr::filter(self_def != "etero") %>%
                          mutate(
                            practice = gsub(pattern = "_", replacement = " ", x = practice),
                            practice = tools::toTitleCase(practice),
                            practice = as.factor(practice),
                            practice = fct_relevel(practice,
                                                   "Insertive", "Oral", "Masturbation", "Finger", "Anal",
                                                   "Petting Noinsertive", "Intercrural", "Kink", "Petting Foreplay"),
                            practice = gsub(pattern = "Finger", replacement = "Other\nmasturbation", x = practice)),
       aes(x = self_def, y = populProp,
           ymax = confInt_up, ymin = confInt_low,
           color = self_def)) +
  geom_hline(yintercept = 1) +
  facet_wrap(practice ~ .) +
  geom_point() +
  geom_errorbar(width = .25) +
  scale_color_discrete(type = c("#eb9b34", "#2828ed")) +
  coord_cartesian(ylim = c(.04, .96)) +
  scale_y_continuous(breaks = seq(from = 0, to = 1, by = .1)) +
  labs(y = "proportion", x = "self identification") +
  theme_pubclean() +
  theme(panel.border = element_rect(color = "black", fill = NA),
        legend.position = "none")
```


::::::::{.landscape data-latex=""}

```{r}
popul_pract %>%
  dplyr::filter(self_def != "etero") %>%
  as.data.frame() %>%
  mutate_at(.vars = c("populProp", "confInt_low", "confInt_up"),
            .funs = round, digits = 4, .cols = NULL) %>%
  mutate(
    confInt = paste0("[", confInt_low * 100, "%, ", confInt_up * 100, "%]"),
    practice = gsub(pattern = "_", replacement = " ", x = practice),
    practice = tools::toTitleCase(practice),
    self_def = tools::toTitleCase(self_def)) %>%
  dplyr::select(-confInt_low, -confInt_up) %>%
  rename(
    `Self-Definition` = self_def,
    Practice = practice,
    `Incidence` = populProp,
    `CI95%` = confInt) %>%
  mutate(
    Incidence = as.character(Incidence * 100),
    Incidence = paste0(Incidence, "%")) %>%
  rename(Frequency = yes) %>%
  dplyr::select(-no) %>%
  pivot_wider(names_from = "Self-Definition", values_from = c(Frequency, Incidence, `CI95%`)) %>%
  dplyr::select(
    "Practice", 
    "Frequency_Bisexual", "Incidence_Bisexual", "CI95%_Bisexual", 
    "Frequency_Lesbian", "Incidence_Lesbian", "CI95%_Lesbian") %>%
  apa(title = "Prevalence of Each Practice within Self-Definitions") %>%
  tab_spanner(label = "Bisexual",
              columns = c("Frequency_Bisexual", "Incidence_Bisexual", "CI95%_Bisexual"), replace = TRUE) %>%
  tab_spanner(label = "Lesbian",
              columns = c("Frequency_Lesbian", "Incidence_Lesbian", "CI95%_Lesbian"))
```


::::::::

```{r}
#fancy radar plot
radarPlot <- popul_pract %>%
  dplyr::filter(self_def != "etero") %>%
  mutate(self_def = as.factor(self_def),
         practice = as.factor(practice)) %>%
  dplyr::select(self_def, practice, populProp) %>%
  spread(key = "practice", value = "populProp") %>%
  dplyr::select(
    self_def,
    insertive, oral, masturbation, finger, anal,
    petting_noinsertive, intercrural, kink, petting_foreplay
    ) %>%
  ggradar(
    #axis labels (to match variables order in the dataset)
    axis.labels = 
      c(
        "Insertive", "Oral", "Masturbation", "Other\nmasturbation", "Anal",
        "Petting Noinsertive", "Intercrural", "Kink", "Petting Foreplay"),
    #colors
    group.colours = c("#eb9b34", "#2828ed"),
    #
    grid.label.size = 5,  # Affects the grid annotations (0%, 50%, etc.)
    axis.label.size = 3, # Afftects the names of the variables
    group.point.size = 1, # Simply the size of the point
    legend.text.size = 9,
  ) +
  theme(
    legend.position = c(1, -.15),
    legend.justification = c(1, 0),
    legend.key = element_rect(fill = NA, color = NA),
    legend.background = element_blank())
radarPlot
```

```{r}
#store plots
png(filename = "descPlot.png", width = 800, height = 400)
incidencePlot + scale_color_grey() + radarPlot + scale_color_grey()
dev.off()
```


\newpage

## Pairwise comparisons (sex-orientation within practice)  

```{r}
practices_pairwiseComp <- expand.grid(
  "practice" = unique(popul_pract$practice),
  "groupA" = c("bisexual", "lesbian"),
  "groupB" = c("bisexual", "lesbian")) %>%
  as_tibble() %>%
  dplyr::filter(groupA != groupB) %>%
  arrange(practice) %>%
  mutate(
    compar = paste(groupA, groupB, sep = "-"),
    map_central = NA,
    confInt_low = NA, 
    confInt_up = NA, 
    BF_ab = NA)
for(i in 1:nrow(practices_pairwiseComp)){
  #extract info
  prct <- practices_pairwiseComp[i, "practice"] %>% unlist() %>% as.character() %>% unname()
  gA <- practices_pairwiseComp[i, "groupA"] %>% unlist() %>% as.character() %>% unname()
  gB <- practices_pairwiseComp[i, "groupB"] %>% unlist() %>% as.character() %>% unname()
  #compute posterior of the difference
  posterior_diff <- posteriorSamples[[gA]][[prct]] - posteriorSamples[[gB]][[prct]] 
  #compute ci
  diffCi <- ci(x = posterior_diff, method = "HDI")
  diffMap <- map_estimate(posterior_diff)
  #compute BF (proportion of samples above 0 / proportion of samples below 0)
  bf <- mean(posterior_diff > 0) / mean(posterior_diff <= 0)
  #store
  practices_pairwiseComp[i, "map_central"] <- diffMap%>% as.numeric() %>% round(digits = 2)
  practices_pairwiseComp[i, "confInt_low"] <- diffCi$CI_low
  practices_pairwiseComp[i, "confInt_up"] <- diffCi$CI_high
  practices_pairwiseComp[i, "BF_ab"] <- bf
  #clean
  rm(prct, gA, gB, posterior_diff, diffCi, bf, diffMap)
};rm(i)
practices_pairwiseComp <- practices_pairwiseComp %>%
         mutate(compar_lab = paste0(compar, " (BF=", round(x = BF_ab, digits = 2), ")"),
                practice = gsub(pattern = "_", replacement = " ", x = practice),
                practice = tools::toTitleCase(practice),
                compar_lab = gsub(pattern = "=Inf", replacement = "=100000", x = compar_lab))
bfPlot <- ggplot(data = practices_pairwiseComp %>%
                   mutate(
                     practice = gsub(pattern = "_", replacement = " ", x = practice),
                     practice = tools::toTitleCase(practice),
                     practice = as.factor(practice),
                     practice = fct_relevel(practice,
                                            "Insertive", "Oral", "Masturbation", "Finger", "Anal",
                                            "Petting Noinsertive", "Intercrural", "Kink", "Petting Foreplay"),
                     practice = gsub(pattern = "Finger", replacement = "Other-masturbation",
                                     x = practice)),
       aes(y = compar_lab, x = map_central,
           xmax = confInt_up, xmin = confInt_low)) +
  geom_point() +
  geom_errorbar(width = .25) +
  geom_vline(xintercept = 0, lty = "dashed") +
  scale_x_continuous(breaks = seq(from = -1, to = 1, by = .1)) +
  facet_wrap(practice ~ ., scales = "free_y", ncol = 1) +
  labs(y = "comparison", x = "posterior difference") +
  theme_pubclean() +
  theme(panel.border = element_rect(color = "black", fill = NA))
bfPlot
```

```{r}
png(filename = "bayesFactors.png", width = 600, height = 600)
bfPlot
dev.off()
```

\newpage

```{r}
practices_pairwiseComp %>%
  dplyr::filter(compar == "lesbian-bisexual") %>%
  as.data.frame() %>%
  dplyr::select(-groupA, -groupB) %>%
  mutate(
    confInt_low = round(x = confInt_low, digits = 2),
    confInt_up = round(x = confInt_up, digits = 2),
    BF_ab = round(x = BF_ab, digits = 3),
    BF_ba = round(x = 1 / BF_ab, digits = 3),
    BF_ab = ifelse(test = is.infinite(BF_ab), yes = 100000, no = BF_ab),
    BF_ba = ifelse(test = is.infinite(BF_ba), yes = 100000, no = BF_ba),
    BF_ab = round(BF_ab, digits = 2),
    BF_ba = round(BF_ba, digits = 2),
  ) %>%
  mutate(
    confInt = paste0("[", confInt_low, ", ", confInt_up, "]"),
    practice = gsub(pattern = "_", replacement = " ", x = practice),
    practice = tools::toTitleCase(practice),
    compar = gsub(pattern = "-", replacement = " ", x = compar),
    compar = tools::toTitleCase(compar),
    compar = gsub(pattern = " ", replacement = "-", x = compar)) %>%
  dplyr::select(-confInt_low, -confInt_up, -compar) %>%
  dplyr::select(practice, map_central, confInt, BF_ab, BF_ba) %>%
  rename(
    Practice = practice,
    MAP = map_central,
    Difference = confInt,
    `BF [LB]` = BF_ab,
    `BF [BL]` = BF_ba) %>%
  apa(title = "Posterior Differences of Pairwise Comparisons across Self-Definitions") %>%
  tab_footnote(footnote = "Posterior Distributions (and their differences) are based on 100000 draws. If all draws of one distribution are above (or below) the draws from the other distribution, the Bayes Factor is assumed to be exactly the number of draws (or 0).")
```

\newpage

## Networks

```{r}
#create dataset
tidyDat <- dat %>%
  dplyr::filter(self_def != "etero") %>% #exclude etero (too few obs)
  dplyr::select(self_def, relation,
                insertive, oral, masturbation, finger, anal,
                intercrural, kink, petting_noinsertive, petting_foreplay) %>%
  mutate(
    relation = gsub(pattern = "[0-9]_", replacement = "", x = relation))
#explore near-zero variance variables
tidyDat %>% 
  dplyr::select(-relation) %>%
  group_by(self_def) %>%
  summarise(
    insertive = var(insertive) %>% round(digits = 2),
    oral = var(oral) %>% round(digits = 2),
    masturbation = var(masturbation) %>% round(digits = 2),
    finger = var(finger) %>% round(digits = 2),
    anal = var(anal) %>% round(digits = 2),
    intercrural = var(intercrural) %>% round(digits = 2),
    kink = var(kink) %>% round(digits = 2),
    petting_noinsertive = var(petting_noinsertive) %>% round(digits = 2),
    petting_foreplay = var(petting_foreplay) %>% round(digits = 2))
```

masturbation and oral have near-zero variance in one of the two groups

```{r}
#split datasets into groups
biDat_all <- tidyDat %>% dplyr::filter(self_def == "bisexual") %>%
  dplyr::select(-masturbation, -oral) %>% #near-zero variance
  dplyr::select(-self_def, -relation) %>%
    rename(
      "Insertive" = insertive,
      "Finger" = finger,
      "Anal" = anal,
      "Petting Noinsertive" = petting_noinsertive,
      "Intercrural" = intercrural, 
      "Kink" = kink,
      "Petting Foreplay" = petting_foreplay) %>%
  dplyr::select(
    "Insertive", "Finger", "Anal", "Petting Noinsertive", 
    "Intercrural", "Kink", "Petting Foreplay")
lesbianDat_all <- tidyDat %>% dplyr::filter(self_def == "lesbian") %>%
  dplyr::select(-masturbation, -oral) %>% #near-zero variance
  dplyr::select(-self_def, -relation) %>%
    rename(
      "Insertive" = insertive,
      "Finger" = finger,
      "Anal" = anal,
      "Petting Noinsertive" = petting_noinsertive,
      "Intercrural" = intercrural, 
      "Kink" = kink,
      "Petting Foreplay" = petting_foreplay) %>%
  dplyr::select(
    "Insertive", "Finger", "Anal", "Petting Noinsertive", 
    "Intercrural", "Kink", "Petting Foreplay")
#subset groups
biDat <- biDat_all %>% dplyr::select(Finger, Kink, Intercrural)
lesbianDat <- lesbianDat_all %>% dplyr::select(Finger, Kink, Intercrural)
#fit networks
biIsing <- IsingFit(x = biDat, AND = FALSE, plot = FALSE) #fit Ising model (for binary data)
lesbianIsing <- IsingFit(x = lesbianDat, AND = FALSE, plot = FALSE) #fit Ising model (for binary data)
#plot networks
layout(t(1:2)) #set layout
biNet_plot <- qgraph(biIsing$q,
                     layout = "circular",
                     labels = biIsing$weiadj %>% colnames(),
                     edge.labels = TRUE,
                     edge.label.cex = 1.5, label.cex = 1.5,
                     labels = tools::toTitleCase(gsub(pattern = "_", replacement = "\n", x = biIsing$q$labels))) %>%
  plot()
title("Bisexual", adj = 0.5, line = 2)
lesbianNet_plot <- qgraph(lesbianIsing$q,
                          layout = "circular",
                          labels = lesbianIsing$weiadj %>% colnames(),
                          edge.labels = TRUE,
                          edge.label.cex = 1.5, label.cex = 1.5,
                          labels = tools::toTitleCase(gsub(pattern = "_", replacement = "\n", x = lesbianIsing$q$labels))) %>%
  plot()
title("Lesbian", adj = 0.5, line = 2)
```

```{r}
#store network image
png(filename = "networks.png", width = 1000, height = 600)
par(cex.main = 2.5)
layout(t(1:2)) #set layout
biNet_plot <- qgraph(biIsing$q,
                     layout = "circular",
                     labels = c("Other\nmasturbation", "Kink", "Intercrural"),
                     edge.labels = TRUE,
                     edge.label.cex = 1.5, label.cex = 2, edge.color = "darkgrey",
                     labels = tools::toTitleCase(gsub(pattern = "_", replacement = "\n", x = biIsing$q$labels))) %>%
  plot()
title("Bisexual", adj = 0.5, line = 2.25)
lesbianNet_plot <- qgraph(lesbianIsing$q,
                          layout = "circular",
                          labels = c("Other\nmasturbation", "Kink", "Intercrural"),
                          edge.labels = TRUE,
                          edge.label.cex = 1.5, label.cex = 2, edge.color = "darkgrey",
                          labels = tools::toTitleCase(gsub(pattern = "_", replacement = "\n", x = lesbianIsing$q$labels))) %>%
  plot()
title("Lesbian", adj = 0.5, line = 2.25)
dev.off()
```


Network Comparison Test.  

$$H_{0}: same \space \space connectivity$$  
  
$$H_{1}: different \space \space connectivity$$  
  
  
```{r}
biLesbo_nct <- NetworkComparisonTest::NCT(
  data1 = biDat, data2 = lesbianDat,
  test.centrality = TRUE,
  test.edges = TRUE,
  it = 1000, binary.data = TRUE)
```

Results

```{r}
biLesbo_nct
```

Based on the Network Comparison Test (global strength invariance), the two networks have the same connectivity.  

\newpage

## Test individual edges across networks  

```{r}
biLesbo_nct$einv.pvals %>% 
  mutate(
    p_adj = p.adjust(p = `p-value`, method = "bonferroni"),
    p_adj = round(p_adj, digits = 2),
    `p-value` = round(`p-value`, digits = 2),
    Var1 = tools::toTitleCase(gsub(pattern = "_", replacement = " ", x = Var1)),
    Var2 = tools::toTitleCase(gsub(pattern = "_", replacement = " ", x = Var2)),
    ) %>%
  arrange(Var1, Var2) %>%
  rename(
    `Variable 1` = Var1,
    `Variable 2` = Var2,
    `Adj. p-value` = p_adj) %>%
  apa(title = "Edges Comparisons across Networks") %>%
  tab_footnote(footnote = "P-values adjusted using Bonferroni correction.")
```

Even without multiple comparisons adjustment, no edge is significantly different across networks
